Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-11-05 ms.tex
Finishing changes to scaling with line center optical depth section

% Phil's edit:
To estimate the scaling of $H_{\rm bc}$ with $\tau_0$, a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$ is used in Equations 16 and 17. In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find

%% TODO: Exclude this entirely or incorporate with Phil's edit?
%To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$. In this limit, $J_{\rm bc} \approx \sqrt{3} H_0$ from Eq. \ref{eq:bc2}. We evaluate Eq. \ref{eq:Jbc} at $r=R$ and solve for the Fourier coefficients, $A(s)$. These are then used in Eq. \ref{eq:Hbc} to find $H_{\rm bc}(R, \sigma)$. Dividing by the contribution from $H_0$, we obtain the proportionality
\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases.

The location of the spectral peak of the distribution is
\be \label{eq:tau_peak_scaling}
x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
\ee
Hence, the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$. For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$. Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$. Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} {\sim} 10^5$. Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases. Additionally, the optical depth at $x_{\rm peak}$ goes as $(a\tau_0)^{1/3}$, so photons here become optically thin when $a\tau_0 {\sim} 1$.

>>>>

We now estimate the scaling of $H_{\rm bc}$ with $\tau_0$. In the limit $J_{\rm bc} \gg H_{\rm bc}$, we find that $J_{\rm bc} {\sim} H_0$ from Equation \ref{eq:bc2}. We  calculate $H_{\rm bc}$ from $J_{\rm bc}$ using Equation \ref{eq:Hbc} and introduce a change of variables to $\bar{\sigma} =  \sigma/\tau_0$ and $\bar{s}=s \tau_0$. The ratio of $H_{\rm bc}$ and $H_0$ is then proportional to $s/(\phi \Delta)$. In the line wing, $\phi \approx a / (\pi x^2 \Delta)$ according to Eq. \ref{eq:line_profile_approx}, and we must choose an appropriate value to insert for $x$. Our dimensionalization $\bar\sigma = \sigma / \tau_0$ implies that $\sigma {\sim} \tau_0$, which, from Equation \ref{eq:int_change_of_variables}, gives us the characteristic frequency
\be \label{eq:tau_peak_scaling}
x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
\ee
This is the location of the spectral peak of the distribution. Similarly, $s {\sim} 1/\tau_0$ from the change of variables, and for the ratio of $H_{\rm bc}$ and $H_0$ we find

\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
At large $\tau_0$, it is expected that the correction term will be small, but it will become increasingly important as $\tau_0$ decreases. From Equation \ref{eq:tau_peak_scaling}, we see that the analytic solution of the transfer equation is only valid when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$. For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$. Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$. Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value at which the peak of the spectrum falls at the Doppler core boundary, which is $\tau_{\rm cp} \approx 10^5$. Hence $H_{\rm bc}/H_0 {\sim} (\tau_{\rm cp}/\tau_0)^{1/3}$ is large at $\tau_0 \leq \tau_{\rm cp}$ and decreases relatively slowly as $\tau_0$ increases. Additionally, the optical depth at $x_{\rm peak}$ is proportional to $(a\tau_0)^{1/3}$, so photons here become optically thin when $a\tau_0 {\sim} 1$.
